---
title: "Kermit Perceptions Rank-Based Test"
author: "Chase Brewster"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey Kelly.

Hi

I am loading packages, data, and intial data exploration (Kelly)
```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv") 

score.pre_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 5) +
  facet_wrap(~Gender)
score.pre_hist

```


Chase the Creator: Perform rank-based comparisons using Mann-Whitney U and Wilcoxon-Signed Rank

Question: Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender, data = .)

# Null Hyp: There is NOT a significant difference in ranks for male and female respondants

# Alt Hyp: There IS a signficant difference in ranks

mwu_kermit
```

"There was no significant difference in ranks for male and female respondeents (W = 155.5, p = 0.4, alpha = 0.05)."

Next Question (Kelly): 

Is there a significant change in Kermit rankings before and after the Bren talk? 

```{r}
#H0: no significant difference in ranks for pre and post talk scores

wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE) 

wsr_kermit


  
  
```

There is no significant difference in ranks for pre and post hoc Kermit scores (p = .3143)
